\documentclass[10pt]{article}
\usepackage[usenames]{color} %used for font color
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\usepackage[utf8]{inputenc} %useful to type directly diacritic characters
\begin{document}
\begin{center}
\title{House prices - Advanced regression techniques}  \
\author{Ryan Neumann} \

    My project is going to be based around housing prices, and how the features of the home influence the price.  Currently, there are hundreds of data points considered when looking to buy a house.  With an almost infinite amount of options, determining the price of a house can be quite a difficult thing to accomplish.   \par

  My idea is to narrow it down to a handful of factors that are able to calculate an accurate price without going through all the hassle of considering ever single one.  Primarily, I would calculate my estimate around the location of the house.  Considering factors such as distance to schools, type of neighborhood, and general environment are essential when looking to buy a home.  Therefore, it would have the greatest influence on the estimated price. \par

  After calculating the price due to location, I would then focus on the details of the house.  This would also help people who are trying to sell their homes.  As a seller, an accurate appraisal of the home is extremely important, especially with the size of the investment on their end.  Determining price points for what a home does and doesn't have will aid in calculating an estimate that will be worth considering.  Each of these would then be added into my algorithm, either raising or lowering the value of the home.  Keeping it simple, I would like to have it either be a 1 or a 0.  Either the home has it, or it doesn't.  This way, it will be a simple algorithm, described to buyers/sellers in a simple way.  The transparency of what is determining the value of the home allows for it to be trusted, having confidence that you know it's worth it's determined value.  \par

  My algorithm will simplify the current real estate business, making it more understandable for those not deeply involved.  As we work towards simplifying complicated issues, the housing market is one that has gone untouched.  Creating a simple algorithm that would accurately determine the value of house, which everyday people understand, is something that could be monumental in progressing the housing market.  
\end{center}
\end{document}